Vector-Similarity based Entity Linking

### 2015-07-08 paper.tex
- added tables with preliminary results. - added a tiny paragraph to the introduction.

\usepackage{lipsum}
\usepackage{todonotes}

@@

\todo[inline]{Write introduction}

@@

>>>>

\usepackage{lipsum}
\usepackage{todonotes}
%\usepackage{booktabs}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

@@

We evaluated V-SEL against the web services of FOX (Federated knOwledge eXtraction framework) and DBpedia Spotlight. FOX is a named entity recognition tool which uses AGDISTIS for entity linking. DBpedia Spotlight employs a four-staged approach which first recognizes and then links entities.

\todo[inline]{Write introduction. Add references to bibliography.}

@@

\begin{table}
\centering
\caption{Results for the AIDA-YAGO dataset.}
\label{table:redirects}
\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
    \hline
    & Fox & DBpedia spotlight & {\acronym}  \\ 
    \hline
    Precision  & 49.27\% & x\% & \textbf{59.33\%} \\
    Recall & 29.68\% & x\% & \textbf{58.56\%} \\
    $F_1$ & 0.37 & x &\textbf{0.59} \\
    \hline
\end{tabularx}
\end{table}

\begin{table}
\centering
\caption{Results for the KORE50 dataset.}
\label{table:redirects}
\begin{tabularx}{0.8\textwidth}{  c  Y  Y  Y }
    \hline
    & Fox & DBpedia spotlight & {\acronym}  \\ 
    \hline
    Precision  & 30.0\% & x\% & 26.16\% \\
    Recall & 20.83\% & x\% & 23.33\% \\
    $F_1$ & 0.25 & x & 0.25 \\
    \hline
\end{tabularx}
\end{table}
